Extended Data

### 2022-02-22 doc/manuscript/Dow_manuscript_Nature.Rmd
fix spelling
Update Dow_manuscript_Nature.Rmd
#111

Seaonal milestones for both canopy foliage phenology and stem growth occurred 6-10 days earlier, on average, at SCBI than at Harvard Forest (Fig. `r DOY_timing`, `r  EDT_phenology_parameters`).
Consistent with the results of Ref[@dorangeville_peak_2021], ring-porous species began growing earlier, reaching the $DOY_{25}$ benchmark earlier (by `r 154-123` days at SCBI and `r 164-132` at Harvard Forest), and their growth was spread over a longer growing season (average $L_{PGS}$ 21 and 19 days longer at SCBI and Harvard Forest, respectively; Fig. `r DOY_timing`, `r  EDF_growth_curves_all`, `r  EDT_phenology_parameters`). 
Peak growing season length was similar across sites, with $L_{PGS}$ being, on average, only two days longer at SCBI for ring-porous species and less than one day longer for diffuse-porous species (`r  EDT_phenology_parameters`).

@@

<!--Hypothesis testing -->
Correlation between the dendrometer band-derived growth parameters ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, $DOY_{g_{max}}$, $L_{PGS}$, $g_{max}$, and $\Delta DBH$}, Fig. `r schematic_summary`) and spring temperatures were assessed using a linear mixed model in a hierarchical Bayesian framework.
Analyses were run for both $T_{max}$ and $T_{min}$, with qualitatively similar results, but we present only results for $T_{max}$, which had overall stronger correlation with growth parameters. 
Mixed effects models were used to test the response of growth parameters to fixed effects of xylem porosity and mean $T_{max}$ (or $T_{min}$) during the CTW, along with random effects of species and of individual tree. 
We ran separate models for each species group at each site, and for the response of all growth parameters to $T_{max}$ (or $T_{min}$). 
This mixed-effect model was run within a hierarchical Bayesian framework and fit using the `rstanarm` R interface to the Stan programming language[@gabry_rstanarm_2020; @stan_development_team_stan_2019]. 
In all cases unless otherwise specified, all prior distributions are set to be the weakly informative defaults. 
<!--
More information on rstanarm's default weakly informative priors:
https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html#default-weakly-informative-prior-distributions
-->

>>>>

Seasonal milestones for both canopy foliage phenology and stem growth occurred 6-10 days earlier, on average, at SCBI than at Harvard Forest (Fig. `r DOY_timing`, `r  EDT_phenology_parameters`).
Consistent with the results of Ref[@dorangeville_peak_2021], ring-porous species began growing earlier, reaching the $DOY_{25}$ benchmark earlier (by `r 154-123` days at SCBI and `r 164-132` at Harvard Forest), and their growth was spread over a longer growing season (average $L_{PGS}$ 21 and 19 days longer at SCBI and Harvard Forest, respectively; Fig. `r DOY_timing`, `r  EDF_growth_curves_all`, `r  EDT_phenology_parameters`). 
Peak growing season length was similar across sites, with $L_{PGS}$ being, on average, only two days longer at SCBI for ring-porous species and less than one day longer for diffuse-porous species (`r  EDT_phenology_parameters`).

@@

<!--Hypothesis testing -->
Correlation between the dendrometer band-derived growth parameters ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, $DOY_{g_{max}}$, $L_{PGS}$, $g_{max}$, and $\Delta DBH$}, Fig. `r schematic_summary`) and spring temperatures were assessed using a linear mixed model in a hierarchical Bayesian framework.
Analyses were run for both $T_{max}$ and $T_{min}$, with qualitatively similar results, but we present only results for $T_{max}$, which had overall stronger correlation with growth parameters. 
Mixed effects models were used to test the response of growth parameters to fixed effects of xylem porosity and mean $T_{max}$ (or $T_{min}$) during the CTW, along with random effects of species and of individual tree. 
We ran separate models for each site, and for the response of all growth parameters to $T_{max}$ (or $T_{min}$). 
This mixed-effect model was run within a hierarchical Bayesian framework and fit using the `rstanarm` R interface to the Stan programming language[@gabry_rstanarm_2020; @stan_development_team_stan_2019]. 
In all cases unless otherwise specified, all prior distributions are set to be the weakly informative defaults. 
<!--
More information on rstanarm's default weakly informative priors:
https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html#default-weakly-informative-prior-distributions
-->
